Test

### 2024-08-21 Test.Rmd
Yet another circle

>>>>

```{r}
# Set up the plotting area
plot(1, type="n", xlab="", ylab="", xlim=c(-20, 20), ylim=c(-20, 20), asp=1)

# Draw three concentric circles with increasing radius
symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")

# Bad trees
symbols(c(15, -5), c(2, 10.5), circles=c(2.5, 3.7), inches=FALSE, add=TRUE, fg = rep("grey", 2))

# good trees 
symbols(c(7, 2,-4), c(-5, 3, -5), circles=c(4, 3, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))

# Centers of trees
points(c(15, -5, 7, 2, -4), c(2, 10.5, -5, 3, -5), pch=as.character(1:5), col="black", cex=0.7) # pch=19

# Add axis lines for reference (optional)
# abline(h=0, v=0, col="gray")

```{r}
# Set up the plotting area
my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-20, 20), ylim=c(-20, 20), asp=1, xaxt="n", yaxt="n")+

  # axis.ticks.x = element_blank(),
  # Draw three concentric circles with increasing radius
  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+

  # Bad trees
  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+

  # good trees 
  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+

  # Centers of trees
  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19

# Sampled point
points(0, 0, pch=19, col="red", cex=0.7) # pch=19
points(-0.2, -0.72, pch="S", col="red", cex=0.7)

# theme(axis.text.x = element_blank(), axis.text.y = element_blank())
#theme(axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
```

```{r}
# Set up the plotting area
my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-16, 16), asp=1, xaxt="n", yaxt="n")+

  # axis.ticks.x = element_blank(),
  # Draw three concentric circles with increasing radius
  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+

  # Bad trees
  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+

  # Good trees 
  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+

  # Centers of trees
  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19

# Sampled point
points(0, 0, pch=19, col="red", cex=0.7) # pch=19
points(-0.2, -0.72, pch="S", col="red", cex=0.7)
```
